\begin{acknowledgements}

\textbf{Personal Acknowledgements:}

First and foremost, I~would like to thank my wife Laura
for her support, understanding, patience, and energy
during my time as a~PhD student, and simply for being at my side.
Without you, I~would not be where I~am today.

I~wholeheartedly thank my two advisors Joaquim Gabarró Vallés
and Michael Hausenblas for their guidance, helpful comments,
informative pointers, and especially
for their constructive criticisms.
The areas of research that I~have tackled in this thesis
are still young and sometimes uncharted territory.
I~am very thankful that the two of you have ventured
on the undertaking of leading me through this thesis.

I~deeply appreciate all the review comments, thoughts, challenging questions,
and, last not least, the \LaTeX~help of my dear friend
and research colleague Ruben Verborgh.
It was, is, and will be an honor to work with you.
My warm thanks also go to Raphaël Troncy and his team
at \mbox{EURECOM} Sophia Antipolis in France
who have helped shape some of the ideas presented in this thesis.

I~would like to thank my former and current managers at Google,
namely N.~Kryvossidis, R.~Ashley, C.~Bouchère, and I.~Sassarini
for their support for my thesis.
A~lot of valuable input for my thesis came in via social networks.
My thanks go out to everyone I have interacted with
around the hashtag \texttt{\#TomsPhD}
on Twitter, \googleplus, and Facebook.

Finally, I~sincerely thank my parents and my brother
who have made me the person I~am today.
My parents have taught me
not to go for the easy choices, even
if at times they may seem tempting,
but instead to try harder and never give up.
This thesis also is for you.

\textbf{Formal Acknowledgements:}

The research presented in this doctoral thesis
was partially supported by the European Commission
under Grant No.~248296 with the European Union (FP7~ICT~STReP)
project \mbox{\emph{I-SEARCH}}.

\vspace{80mm}

\textbf{To cite this document:}

\small
\begin{verbatim}
  @phdthesis{steiner2013thesis,
    author = {Thomas Steiner},
    title  = {Enriching Unstructured Media Content About Events to
              Enable Semi-Automated Summaries, Compilations, and
              Improved Search by Leveraging Social Networks},
    year   = {2013},
    school = {Universitat Polit\`{e}cnica de Catalunya}
  }
\end{verbatim}

\normalsize

\vspace{10mm}
\textbf{Copyright and License:}\\\\
\small \copyright \normalsize 2013 Thomas Steiner\\
Licensed under the Creative Commons Attribution-ShareAlike 3.0 License.\\
\url{http://creativecommons.org/licenses/by-sa/3.0/}

\end{acknowledgements}
