% this file is called up by thesis.tex
% content in this file will be fed into the main document

%: ----------------------- introduction file header -----------------------

\chapter{Appendices}
\appendix

% the code below specifies where the figures are stored
\ifpdf
    \graphicspath{{backmatter/figures/PNG/}{backmatter/figures/PDF/}{backmatter/figures/}}
\else
    \graphicspath{{backmatter/figures/EPS/}{backmatter/figures/}}
\fi

% ----------------------------------------------------------------------
%: ------------------------------- content -----------------------------
% ----------------------------------------------------------------------

\section*{Curriculum Vitæ}}

\begin{cv}{}
\begin{cvlist}{Personal Data}
	\item[]
		Thomas Steiner \\
		Bäckerbreitergang 12,
		20355 Hamburg,
		Germany\\ \\
		Born December 17, 1981 in Freudenstadt
\end{cvlist}
%
\begin{cvlist}{Education}
    \item[2010--2013] \emph{PhD candidate} in Computing, Universitat Politècnica de Catalunya, Barcelona (Spain).
    \item[2005--2007] Double degree \emph{Master of Computer Science},
    Karlsruhe Institute of Technology (Germany) and
    ENSIMAG Grenoble (France).  
    Thesis: 
    \\[0.4\baselineskip]
    \onlyfullcite{steiner2007automatic}
    \item[2002--2005] \emph{Bachelor of Computer Science}, Karlsruhe Institute of Technology (Germany).
	\item[2001] \emph{Final secondary-school examinations}, Isolde-Kurz-Gymnasium Reutlingen (Germany).
\end{cvlist}

\begin{cvlist}{Professional Experience}
    \item[2010--2013] \emph{Research Scientist},
    Google Germany GmbH, Hamburg.
    \\[0.4\baselineskip]
    Worked on the EU
    project \mbox{\emph{I-SEARCH}},
    which created a~novel unified framework for 
    multimedia and multimodal content indexing,
    sharing, search, and retrieval. \mbox{I-SEARCH}
    was the first multimodal search engine able to handle  
    multimedia (text, 2D image, sketch, video,
    3D objects, audio),
    multimodal content (gestures, face expressions),
    combined with real-world information
    (GPS, time, weather).
    \item[2007--2010] \emph{Customer Solutions Engineer}
    at Google Germany GmbH, Hamburg.
    \\[0.4\baselineskip]
    Worked in the Google Technical Services (gTech) team,
    which serves as the primary point of contact for
    Google's global Sales, Business Development, and
    Partnerships teams to support the sales organization
    across all products.
\end{cvlist}

\end{cv}

\clearpage
\section*{Publications}

\begin{itemize}
  \interlinepenalty10000
  \item \onlyfullcite{steiner2014clustering}.
  \item \onlyfullcite{verborgh2013distributedaffordance}.
  \item \onlyfullcite{steiner2013vhsrecording}.
  \item \onlyfullcite{steiner2013nearduplicate}.
  \item \onlyfullcite{steiner2013meteoroid}.
  \item \onlyfullcite{steiner2013addingmeaning}.
  \item \onlyfullcite{steiner2013thesis}.
  \item \onlyfullcite{milicic2013live}.
  \item \onlyfullcite{steiner2013mj}.
  \item \onlyfullcite{van2013named}.
  \item \onlyfullcite{verborgh2013proof}.
  \item \onlyfullcite{verborgh2013semantic}.
  \item \onlyfullcite{steiner2013crop}.
  \item \onlyfullcite{steiner2012addingrealtime}.
  \item \onlyfullcite{verborgh2012functionalcomposition}.
  \item \onlyfullcite{steiner2012sekiathomechallenge}.
  \item \onlyfullcite{steiner2012sekiathome}.
  \item \onlyfullcite{steiner2012definingaesthetic}.
  \item \onlyfullcite{khrouf2012aggregatingsocialmedia}.
  \item \onlyfullcite{verborgh2012missinglinks}.
  \item \onlyfullcite{steiner2012shotdetection}.
  \item \onlyfullcite{steiner2012xkcd37}.
  \item \onlyfullcite{verborgh2012socialdescriptionrevolution}.
  \item \onlyfullcite{verborgh2012capturingthefunctionality}.
  \item \onlyfullcite{khrouf2012confomaton}.
  \item \onlyfullcite{etzold2012contextawarequerying}.
  \item \onlyfullcite{verborgh2012functionaldescriptions}.
  \item \onlyfullcite{steiner2012isearch}.
  \item \onlyfullcite{axenopoulos2012isearch}.
  \item \onlyfullcite{troncy2012mediafragments}.
  \item \onlyfullcite{steiner2012onesizedoesnotfitall}.
  \item \onlyfullcite{verborgh2012restdesc}.
  \item \onlyfullcite{rizzo2012whatfresh}.
  \item \onlyfullcite{verborgh2011descriptionandinteraction}.
  \item \onlyfullcite{steiner2011addingmeaning}.
  \item \onlyfullcite{steiner2011crowdsourcingevent}.
  \item \onlyfullcite{verborgh2011efficientruntime}.
  \item \onlyfullcite{verborgh2011integratingdata}.
  \item \onlyfullcite{steiner2011tweetconsumers}.
  \item \onlyfullcite{steiner2011enrichingunstructured}.
  \item \onlyfullcite{steiner2011fulfilling}.
  \item \onlyfullcite{alduan2011futureinternet}.
  \item \onlyfullcite{daras2011unifiedframework}.
  \item \onlyfullcite{steiner2010howgoogleisusing}.
  \item \onlyfullcite{steiner2010semwebvid}.
  \item \onlyfullcite{steiner2010semwebvidchallenge}.
\end{itemize}